---
bibliography: references.bib
---

```{r}
library(dplyr)
library(ggplot2)
library(leaflet)
library(readxl)
```

## Plot Greenhouse gas emissions data in CO2 equivalent (CO2eq) units for each country in 2019 @usman2021

$\text{Indirect N}_2\text{O Emissions} = \text{N Applied} \times \text{Leaching/Runoff Fraction} \times \text{Emission Factor (N)}$

-   Coding Expalination: Data Preparation: The code filters the emissions data for CO2eq emissions in 2019. GeoJSON Loading: The geographical boundaries are loaded from a GeoJSON file. Data Merging: The emissions data is merged with the geographical boundaries. Interactive Map: leaflet is used to create an interactive map where the color represents the intensity of emissions.

-   Interactive Features: Hover Information: Hovering over a country will display its name and emissions in a popup. Color Legend: A legend will show the distribution of emissions across countries !!.

```{r}

library(rnaturalearth)
library(sf)

# Download country boundaries
world <- ne_countries(scale = "medium", 
                      returnclass = "sf")

st_write(world, 
         "world_countries.geojson", 
         driver = "GeoJSON")

```

```{r}
# Load spatial data (replace with actual file path)
world_map <- st_read("world_countries.geojson")

emissions_data <- read_excel("Global-emission.xlsx")

map_data <- world_map %>%
            left_join(emissions_data, by = c("country_column" = "Area"))

```

```{r}

file_path <- "Global-emission.xlsx"
emissions_data <- read_excel(file_path, sheet = "Worksheet")

emissions_2019 <- emissions_data %>%
  filter(grepl("Emissions \\(CO2eq\\)", Element)) %>%
  select(Area, Y2019) %>%
  rename(Total_Emissions_CO2eq = Y2019)

geojson_file <- "world_countries.geojson"
world_map <- st_read(geojson_file)

map_data <- world_map %>%
  left_join(emissions_2019, 
            by = c("name" = "Area"))

leaflet(map_data) %>%
  addTiles() %>%
  addPolygons(
    fillColor = ~colorQuantile("YlOrRd", 
                               Total_Emissions_CO2eq)(Total_Emissions_CO2eq),
    color = "black", 
    weight = 1, 
    opacity = 1, 
    fillOpacity = 0.7,
    popup = ~paste("Country: ", 
                   name, "<br>",
                   "Total Emissions (kt CO2eq): ", 
                   Total_Emissions_CO2eq)
  ) %>%
  addLegend(
    pal = colorQuantile("YlOrRd",
                        map_data$Total_Emissions_CO2eq),
    values = map_data$Total_Emissions_CO2eq,
    title = "GHG Emissions (kt CO2eq)",
    position = "bottomright"
  )

```

------------------------------------------------------------------------

## 🔥 The Hourly Heatmap (Better with many column data)

The heatmap provides a clear visual representation of the CO2 emission trends across Southeast Asia, revealing the environmental impact of economic activities in the region. 😄😄

```{r}

library(ggplot2)
library(dplyr)
library(tidyr)
library(viridis)  
library(ggtext)
library(RColorBrewer)


# List of Southeast Asian countries
southeast_asia <- c("Brunei Darussalam", 
                    "Cambodia", 
                    "Indonesia", 
                    "Malaysia", 
                    "Myanmar", 
                    "Philippines", 
                    "Singapore", 
                    "Thailand", 
                    "Timor-Leste", 
                    "Viet Nam")

sea_emissions_data <- co2_emissions_long %>% filter(Area %in% southeast_asia)

breaks <- c(0, 5e6, 1e7, 1.5e7)
labels <- scales::scientific(breaks)

ggplot(sea_emissions_data, aes(x = Year, 
                               y = Area, 
                               fill = Emissions)) +
  
  geom_tile(color = "white", size = 0.1) +  
  scale_fill_gradientn(colors = rev(brewer.pal(9, "Spectral")), 
                       na.value = "gray90", 
                       breaks = breaks, labels = labels, 
                       name = "Emissions (kt)") +   
  theme_minimal(base_size = 15) +  
  labs(title = 
  "<span style='color:#e31a1c;'>CO2 Emissions</span> by Year in <b>Southeast Asia</b>",
       x = NULL,
       y = NULL) +  
  theme(
    axis.text.x = element_text(angle = 45, 
                               vjust = 1, 
                               hjust=1, 
                               color = "gray20"),  
    axis.text.y = element_text(size = 12, 
                               color = "gray20"),  
    plot.title = element_markdown(hjust = 0.5, 
                                  size = 20, 
                                  face = "bold"),  
    panel.grid.major = element_blank(),  # Remove gridlines
    panel.grid.minor = element_blank(),  # Remove minor gridlines
    panel.background = element_blank(),  # Remove the background rectangle
    plot.background = element_blank(),   # Remove the plot background rectangle
    legend.position = "right"            # Position the legend on the right
  )

```

The observed trends in CO2 emissions across Southeast Asia are closely linked to economic growth, energy consumption, and industrial activities. The region has undergone rapid development, particularly in the latter half of the 20th century, leading to increased fossil fuel consumption, deforestation, and urbanization—all key contributors to rising CO2 emissions

**\
Indonesia’s Role in Regional Emissions**

:   Indonesia's dominant position in terms of emissions is partly due to its large-scale deforestation activities, particularly for palm oil production. Deforestation and peatland drainage release significant amounts of CO2, making Indonesia one of the largest greenhouse gas emitters in the region (World Resources Institute, 2020).

Implication

:   Despite the economic benefits of industrialization, the environmental costs are significant, highlighting the need for sustainable development practices, investment in renewable energy, and effective forest management policies (International Energy Agency, 2021; UNFCCC, 2020).

------------------------------------------------------------------------
